---
title: "Final Project"
author: "Ping hu"
date: "1/15/2019"
output: slidy_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Requirement

- Form of input (widget: textbox, radio button, checkbox, ...)
- Operation on the ui input in sever.R
- Reactive output from server calculations
- Enough documentation for novice user.
- Documentation at the Shiny website itself.
- Deploy the application on Rstudio's shiny server: https://pinglearning.shinyapps.io/shiny_2_files/
- Share application link, pasting into provided text box
- Share your server.R and ui.R code on github
https://github.com/pinghu/courseraLearning
- Interactive Presentation Located at:
https://pinglearning.shinyapps.io/Final_Project_Presentation/_w_14b7b9f2/#(1)

## ui.R Code
```{r ui, echo = TRUE, eval=FALSE}
library(shiny)
shinyUI(fluidPage(
  titlePanel("Homewrk Project 1-12-2019 Ping Hu"),
  pageWithSidebar(
    headerPanel('Iris k-means clustering, please choose parameter below to see the resulted clusters'),
    sidebarPanel(
      selectInput('xcol', 'X Variable', names(iris)),
      selectInput('ycol', 'Y Variable', names(iris),
                  selected=names(iris)[[2]]),
      numericInput('clusters', 'Cluster count', 3,min = 1, max = 9)
    ),
    mainPanel( plotOutput('plot1'))
  )
))
```
## server.R code


```{r server, echo=TRUE, eval=FALSE}
library(shiny)
shinyServer(
  function(input, output, session) {
    selectedData <- reactive({
      iris[, c(input$xcol, input$ycol)]
    })
    clusters <- reactive({
      kmeans(selectedData(), input$clusters)
    })
    output$plot1 <- renderPlot({
      palette(c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3",
                "#FF7F00", "#FFFF33", "#A65628", "#F781BF", "#999999"))
      par(mar = c(5.1, 4.1, 0, 1))
      plot(selectedData(),
           col = clusters()$cluster,
           pch = 20, cex = 3)
      points(clusters()$centers, pch = 4, cex = 4, lwd = 4)
    })
  }
)
```

## Shiny Server Interactive Plot

```{r present, echo=FALSE}
library(shiny)

# Define UI for application that draws a histogram
ui <- fluidPage(
  pageWithSidebar(
    headerPanel('Iris k-means clustering'),
    sidebarPanel(
      selectInput('xcol', 'X Variable', names(iris)),
      selectInput('ycol', 'Y Variable', names(iris),
                  selected=names(iris)[[2]]),
      numericInput('clusters', 'Cluster count', 3,
                   min = 1, max = 9)
    ),
    mainPanel(
      plotOutput('plot1')
    )
  )
)


# Define server logic required to draw a histogram
server <- function(input, output, session) {
    
    # Combine the selected variables into a new data frame
    selectedData <- reactive({
      iris[, c(input$xcol, input$ycol)]
    })
    
    clusters <- reactive({
      kmeans(selectedData(), input$clusters)
    })
    
    output$plot1 <- renderPlot({
      palette(c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3",
                "#FF7F00", "#FFFF33", "#A65628", "#F781BF", "#999999"))
      
      par(mar = c(5.1, 4.1, 0, 1))
      plot(selectedData(),
           col = clusters()$cluster,
           pch = 20, cex = 3)
      points(clusters()$centers, pch = 4, cex = 4, lwd = 4)
    })
}

# Run the application 
shinyApp(ui = ui, server = server)


```

